Parsing mPFC: A Joint Meta-Analytic and Graph Theoretic Approach

### 2018-12-11 Manuscript.Rmd
The final dataset was run, and this script will produce the pdf fine (was running into issues plotting the mixed effects before, corrupting the pdf)

### Testing grounds
# this part compares the distribution of Fiedler values for DMN and nonDMN
# note: remove filter(y > 0) for 'full brain'
# First plot compares the median FV between communities across subjects
test <- do.call(rbind, Summaries)
ecdfPCC <- test %>%
          mutate(SubjID = rep(subjList, each = nVertices),
                 FV_abs = abs(FiedlerVec),
                 Community = ifelse(FiedlerBinary == 0, "nonDMN", "DMN")) %>%
          filter(y < 0) %>%
          ggplot(aes(FV_abs, group = interaction(SubjID, Community), color = Community)) +
          stat_ecdf(alpha = 0.3) +
          #scale_color_manual(values = c("Yellow", "Red")) +
          xlim(0,0.05) +
          geom_vline(xintercept = 0.009, lty = 2) +
          labs(title = "Per-subject ECDF of Fiedler values: PCC") +
          theme_classic()

ecdfPFC <- test %>%
          mutate(SubjID = rep(subjList, each = nVertices),
                 FV_abs = abs(FiedlerVec),
                 Community = ifelse(FiedlerBinary == 0, "nonDMN", "DMN")) %>%
          filter(y > 0) %>%
          ggplot(aes(FV_abs, group = interaction(SubjID, Community), color = Community)) +
          #scale_color_manual(values = c("Yellow", "Red")) +
          stat_ecdf(alpha = 0.3) +
          xlim(0,0.05) +
          labs(title = "Per-subject ECDF of Fiedler values: PFC") +
          geom_vline(xintercept = 0.009, lty = 2) +
          theme_classic()

ecdfALL <- test %>%
  mutate(SubjID = rep(subjList, each = nVertices),
         FV_abs = abs(FiedlerVec),
         Community = ifelse(FiedlerBinary == 0, "nonDMN", "DMN")) %>%
  ggplot(aes(FV_abs, group = interaction(SubjID, Community), color = Community)) +
  #scale_color_manual(values = c("Yellow", "Red")) +
  stat_ecdf(alpha = 0.5) +
  xlim(0,0.05) +
  labs(title = "Per-subject ECDF of Fiedler values") +
  geom_vline(xintercept = 0.009, lty = 2) +
  theme_classic()

@@

# Put together a data frame to plot Fiedler vec x proprtion DMN
allSummaries <- do.call(rbind, Summaries)
allSummaries$SubjID <- rep(subjList, each = nrow(Summaries[[1]]))

@@

@@

``` {r Partition comparison: halves, echo=FALSE, message = FALSE, cache = TRUE}
# Load data
setwd('./Summary_halves/')
temp <- list.files(pattern = "*_finalSummary.csv")
subjList_halves <- sapply(temp, substring, first=1, last=9)
Summaries_halves <- lapply(temp, read.csv)
selectSubj <- seq(20)

# Before thresholding, capture within/between daily comparisons for FV vs correlation analysis (only for daily)
# Select a subsection of participants for plotting
Summaries_halves_plot <- Summaries_halves[selectSubj]
unthreshComm_PFC_halves_plot <- lapply(Summaries_halves_plot, "[", i = !posteriorIndx, j =)
unthreshComm_PFC_halves <- lapply(Summaries_halves, "[", i = !posteriorIndx, j =)

@@

# Select a submatrix with the best-performing subjects to show on the matrix figures
# These will be also displayed on the session matrix
# This way I don't have to recompute stuff
tmp <- data_frame(SubjID = subjList,
                  DailyARI = Halves_PFCComparison[[1]])
best <- tmp %>% top_n(10, wt = DailyARI) %>% arrange(DailyARI)
bestindx <- substr(subjList_halves,1,6) %in% best$SubjID

@@

# Load the correlation-based maps (this might be ok to move to the cor vs comm chunk)
temp <- list.files(pattern = "*_corHalves.csv")
Correlation_halves <- lapply(temp, read.csv, header = F)
Correlation_halves_plot <- Correlation_halves[bestindx] # CHANGE TO THE ACTUAL SUBJECTS
```

@@

```{r Meta-analysis ROIs (Fig. 1), out.width = "50%", fig.align = "center", fig.cap= "Figure 1. Template atlas from Glasser et al. (2016) (top), as well as the common and unique brain regions associated with DMN and subjective value (bottom). Overlapping ROIs (in blue) were defined as the common brain regions that were significantly present in their respective literatures, while a single DMN-specific region (7m, in red) was identified from a permutation analysis comparing these literatures."}
# Change to inflated eventually
include_graphics("./Images/ROIS2.png")
```

@@

``` {r Partition comparison: all cross-method agreement (Fig. 3), fig.align="center", fig.width=3.5, fig.height=3.5, echo=FALSE, message = FALSE, cache = TRUE, fig.cap = "Figure 3. Distribution of ARI indices when comparing modularity and spectral partitioning. The distribution shows overall high agreement. (Will probably remove this figure)"}
RI_within_plot <- ggplot(data = RI_all_within, aes(Index)) + 
        geom_density(fill = Cols[3]) + 
        xlim(0,1) + 
        labs(x = "Adj. Rand Index") +
        theme_classic()
RI_within_plot
```

``` {r Partition comparison: all 2 (Fig. 4), fig.align="center", out.width = "40%", fig.cap = "Figure 4. Similarity matrix showing ARI values among all subjects for PCC (lower triangle) and mPFC (upper triangle) separately. PCC is well aligned across individuals, while mPFC shows clear topographical heterogeneity.", echo=FALSE, message = FALSE, cache = TRUE}
par(xpd=T)
corrplot(RI_PCC,
         is.corr = F, 
         method = "color",
         type = "lower", 
         tl.pos = "n", 
         tl.cex = 0.1, 
         #cl.lim = c(0,1),
         cl.length = 3,
         addgrid.col = "grey99",
         cl.pos = "r",
         mar = c(1,1,2,0))
corrplot(RI_PFC, 
         is.corr = F, 
         method = "color", 
         type = "upper", 
         tl.pos = "n", 
         tl.cex = 0.1,
         cl.pos = "n",
         addgrid.col = "grey90",
         mar = c(1,1,2,0), 
         add = T)
segments(0.5,0.5,0.5,100.5, lwd = 2)
segments(0.5,0.5,100.5,0.5, lwd = 2)
segments(0.5,100.5,100.5,100.5, lwd = 2)
segments(100.5,0.5,100.5,100.5, lwd = 2)
mtext(expression(bold("Subject Partitions")), line = 3)
mtext(expression(bold("Subject Partitions")), side = 2, line = -0.8)
mtext(expression(bold("mPFC")), line = 2, at = par("usr")[1]+0.73*diff(par("usr")[1:2]), col = "steelblue4")
mtext(expression(bold("PCC")), side = 1, line = 4, at = par("usr")[1]+0.18*diff(par("usr")[1:2]), col = "steelblue4")

@@

``` {r Partition comparison: halves (Fig. 5), fig.align="center", out.width = "60%", fig.cap = "Figure 5. Similarity matrices for 10 example participants showing pattern agreement across days for the whole partition (left), and for PCC and mPFC separately (right). These figures show high agreement within (but not between) subjects, with mPFC again showing significant variability.", echo=FALSE, message = FALSE, cache = TRUE}
# plots
par(mfrow=c(1,2))
corrplot(RI_all_between_halves_plot, 
         is.corr = F, 
         method = "color",
         addgrid.col = "grey90",
         tl.pos = "n", 
         tl.col = "black",
         tl.cex = 0.1,
         cl.pos = "n",
         #cl.lim = c(0,1),
         cl.length = 3,
         mar = c(1.1,1.1,1.1,1.1))
# segments(0.5,0.5,0.5,20.5, lwd = 2)
# segments(0.5,0.5,20.5,0.5, lwd = 2)
# segments(0.5,20.5,20.5,20.5, lwd = 2)
# segments(20.5,0.5,20.5,20.5, lwd = 2)
mtext(expression(bold("Subjects (Day 1 and Day 2)")), line = 1)
mtext(expression(bold("Subjects (Day 1 and Day 2)")), side = 2, line = 3)
corrplot(RI_PCC_halves_plot, 
         is.corr = F,     
         method = "color",
         type = "lower", 
         tl.pos = "n", 
         #cl.lim = c(0,1),
         cl.pos = "r",
         addgrid.col = "grey90",
         cl.length = 3)
corrplot(RI_PFC_halves_plot, 
         is.corr = F, 
         method = "color",
         type = "upper", 
         tl.pos = "n", 
         cl.pos = "n", 
         addgrid.col = "grey90",
         add = T)
mtext(expression(bold("Subjects (Day 1 and Day 2)")), line = 1)
mtext(expression(bold("mPFC")), line = -0.15, at = par("usr")[1]+0.8*diff(par("usr")[1:2]), col = "steelblue4")
mtext(expression(bold("PCC")), side = 1, line = 0.6, at = par("usr")[1]+0.09*diff(par("usr")[1:2]), col = "steelblue4")
```

``` {r Partition comparison: halves ratios (Fig. 6), fig.align="center", fig.width=3, fig.height=3, fig.cap = "Figure 6. mPFC displays higher within-subject agreement than between subjeccts, as evidenced by a high within/between subject mean ARI. PCC also shows some level of topographical idiosyncrasy (ratio > 1), but significantly lower than mPFC.", echo=FALSE, message = FALSE, cache = TRUE}
# plot
ggplot(data = Halves_RIRatios_summary, aes(Region, RI, fill = Region)) + 
  geom_boxplot(show.legend = F) +
  scale_fill_manual(values = Cols[seq(2)]) + 
  ylim(0, 10) +
  geom_hline(yintercept = 1) +
  labs(y = "ARI Ratio", x = "") + 
  theme_classic(base_size = 14)
```

``` {r Partition comparison: session similarity matrices (Fig. 7), fig.align="center", out.width = "60%", fig.cap = "Figure 7. Similarity matrices showing pattern agreement across sessions for the whole partition (left), and for PCC and mPFC separately (right) (10 example subjects). The pattern from the daily analysis is preserved, with marked individuality for mPFC, but not PCC.", echo=FALSE, message = FALSE, cache = TRUE}
# plot
par(mfrow=c(1,2))
corrplot(RI_all_between_sess_plot, 
         is.corr = F, 
         method = "color", 
         tl.pos = "n", 
         tl.cex = 0.5,
         tl.col = "black", 
         #cl.lim = c(-0.03,1),
         cl.pos = "n",
         cl.length = 3,
         mar = c(1.1,1.1,1.1,1.1), 
         addgrid.col = "grey90")
# segments(0.5,0.5,0.5,40.5, lwd = 2)
# segments(0.5,0.5,40.5,0.5, lwd = 2)
# segments(0.5,40.5,40.5,40.5, lwd = 2)
# segments(40.5,0.5,40.5,40.5, lwd = 2)
mtext(expression(bold("Subjects (Session)")), line = 1)
mtext(expression(bold("Subjects (Session)")), side = 2, line = 3)
corrplot(RI_PCC_sess_plot, 
         is.corr = F, 
         method = "color", 
         type = "lower", 
         tl.pos = "n", 
         tl.cex = 0.5,
         tl.col = "black", 
         #cl.lim = c(0,1),
         cl.length = 3,
         cl.pos = "r", 
         addgrid.col = "grey90")
# segments(0.5,0.5,0.5,20.5, lwd = 2)
# segments(0.5,0.5,20.5,0.5, lwd = 2)
# segments(0.5,20.5,20.5,20.5, lwd = 2)
# segments(20.5,0.5,20.5,20.5, lwd = 2)
corrplot(RI_PFC_sess_plot, 
         is.corr = F, 
         method = "color", 
         type = "upper", 
         tl.pos = "n", 
         tl.col = "black", 
         cl.pos = "n", 
         addgrid.col = "grey90",
         add = T)
mtext(expression(bold("Subjects (Session)")), line = 1)
mtext(expression(bold("mPFC")), line = 0, at = par("usr")[1]+0.8*diff(par("usr")[1:2]), col = "steelblue4")
mtext(expression(bold("PCC")), side = 1, line = 1, at = par("usr")[1]+0.09*diff(par("usr")[1:2]), col = "steelblue4")
```

``` {r Partition comparison: session ratios (Fig. 8), fig.align="center", fig.width=3, fig.height=3, fig.cap = "Figure 8. Whole group ratio between within- and between-subject ARI for mPFC and PCC based on sessions. Consistent with the daily analysis, both regions show idiosyncrasy, with mPFC being significantly more subject-specific.", echo=FALSE, message = FALSE, cache = TRUE}
ggplot(data = Sess_RIRatios_summary, aes(Region, RI, fill = Region)) + 
  geom_boxplot(show.legend = F) +
  scale_fill_manual(values = Cols[seq(2)]) + 
  ylim(0, NA) +
  geom_hline(yintercept = 1) +
  labs(y = "ARI Ratio", x = "") + 
  theme_classic(base_size = 14)
```

``` {r Stability per subject: Overall (Fig. 9), fig.align="center", fig.width=5, fig.height=3, fig.cap = "Figure 9. ARI between communities computed at each sliding epoch and the original partition for all subjects (left), as well as the distribution of ARI standard deviations per subject (right).", echo=FALSE, message = FALSE, cache = TRUE}
# TAKE THE TIME TO BRING THE GGPLOT DEFINITION DOWN HERE EVENTUALLY
grid.arrange(SC_plot, SC_sd_plot, ncol = 2)
```

``` {r Stability per subject: PCC vs mPFC (Fig 10), fig.align="center", fig.width=5, fig.height=4, fig.cap = "Figure 10. ARI between each window and the original pattern for PCC and mPFC separately (left), and the mean per-subject ARI for the whole group (middle). Regardless of the mean ARI, standard deviation remained low for both regions (right).", echo=FALSE, message = FALSE, cache = TRUE}

@@

``` {r Stability per subject: Fiedler vector vs prop. DMN plot (Fig 11), fig.align="center", fig.width=3, fig.height=3, fig.cap = "Figure 11. Relationship between the magnitude of Fiedler vector values and the proportion of affiliations of a vertex with DMN throughout 37 sliding windows. Grey lines denote each subject's association, while the black line shows the fit from a mixed effects logistic regression.", echo=FALSE, message = FALSE}
# Fiedler Vector x proportion of times a vertex was affiliated with DMN
SC_FVvPDMN_plot <- ggplot(data = allSummaries) +
  geom_smooth(aes(FiedlerVec, slidePropDMN, group = SubjID), color = "gray", fill = "gray", show.legend = F, alpha = 0.3) +
  #geom_point(aes(FiedlerVec, slidePropDMN, fill = SubjID), show.legend = F, alpha = 0.05, pch = 21, color = "black") + 
  geom_line(aes(FiedlerVec, FittedVals), alpha = 1, size = 3) +
  labs(x = "Fiedler Vector Values", y = "Proportion of DMN Affiliations") +
  theme_classic()

@@

``` {r Noise Effects: tSNR Comparison (Fig. 12), fig.align="center", fig.width=3, fig.height=3, fig.cap = "Figure 12. Mean tSNR for mPFC and PCC across participants. This measure was derived from the minimally preprocessed fMRI data from the HCP, and thus shows the base level of reltive noise in each region.", echo=FALSE, message = FALSE, cache = TRUE}
# Plot the mPFC SNR vs PCC SNR for each subject (one figure containing all subjects)
snrmeanComp_plot <- ggplot(data = SNR_meanComp$Values, aes(Region, SNR, fill = Region)) +
  geom_boxplot(show.legend = F) +
  scale_fill_manual(values = Cols[seq(2)]) +
  labs(x = "", y = "tSNR") +
  theme(text = element_text(size=35)) +
  theme_classic()
snrmeanComp_plot
```

@@

``` {r Noise Effects: R-sqd vs tSNR (Fig. 14), fig.align="center", fig.width=5, fig.height=3, fig.cap = "Figure 14. Vertex tSNR values across all subjects are correlated with their position along the z-axis in mPFC, with vmPFC showing the lowest tSNR (left). However, R-square values do not show this strong relationship (right), suggesting that the coupling of each vertex is not necessarily influenced by signal noise.", echo=FALSE, message = FALSE, cache = TRUE}
# grid.arrange(v6, v7, ncol = 2)
# par(mfrow = c(1,2))
# smoothScatter(allVariance[allVariance$Region == "mPFC",]$Rsquared, allVariance[allVariance$Region == "mPFC",]$tempZ,
#               xlab = "R-squared Value",
#               ylab = "Z-Coordinate")
# 
# smoothScatter(allVariance[allVariance$Region == "mPFC",]$varCoeff, allVariance[allVariance$Region == "mPFC",]$tempZ,
#               xlab = "Coefficient of Variation (SNR)",
#               ylab = "")

>>>>

### Testing grounds
# this part compares the distribution of Fiedler values for DMN and nonDMN
# note: remove filter(y > 0) for 'full brain'
# First plot compares the median FV between communities across subjects
allSummaries <- do.call(rbind, Summaries)
allSummaries$SubjID <- rep(subjList, each = nVertices) 
ecdfPCC <- allSummaries %>%
          mutate(FV_abs = abs(FiedlerVec),
                 Community = ifelse(FiedlerBinary == 0, "nonDMN", "DMN")) %>%
          filter(y < 0) %>%
          ggplot(aes(FV_abs, group = interaction(SubjID, Community), color = Community)) +
          stat_ecdf(alpha = 0.3) +
          #scale_color_manual(values = c("Yellow", "Red")) +
          xlim(0,0.05) +
          geom_vline(xintercept = 0.009, lty = 2) +
          labs(title = "Per-subject ECDF of Fiedler values: PCC") +
          theme_classic()

ecdfPFC <- allSummaries %>%
          mutate(FV_abs = abs(FiedlerVec),
                 Community = ifelse(FiedlerBinary == 0, "nonDMN", "DMN")) %>%
          filter(y > 0) %>%
          ggplot(aes(FV_abs, group = interaction(SubjID, Community), color = Community)) +
          #scale_color_manual(values = c("Yellow", "Red")) +
          stat_ecdf(alpha = 0.3) +
          xlim(0,0.05) +
          labs(title = "Per-subject ECDF of Fiedler values: PFC") +
          geom_vline(xintercept = 0.009, lty = 2) +
          theme_classic()

ecdfALL <- allSummaries %>%
  mutate(FV_abs = abs(FiedlerVec),
         Community = ifelse(FiedlerBinary == 0, "nonDMN", "DMN")) %>%
  ggplot(aes(FV_abs, group = interaction(SubjID, Community), color = Community)) +
  #scale_color_manual(values = c("Yellow", "Red")) +
  stat_ecdf(alpha = 0.5) +
  xlim(0,0.05) +
  labs(title = "Per-subject ECDF of Fiedler values") +
  geom_vline(xintercept = 0.009, lty = 2) +
  theme_classic()

@@

@@

# Create a smaller dataframe just to plot the fit
# Otherwise, plotting the thousands fitted can place an unnecessary burden on the document
# (at some point, knitting to pdf wouldn't show the logistic plot because of this)
FiedlerVector <- seq(min(allSummaries$FiedlerVec), max(allSummaries$FiedlerVec), length.out = nVertices)
formula <- SC_FVvPDMN_modelSummary$coefficients[1,1] + (SC_FVvPDMN_modelSummary$coefficients[2,1] * FiedlerVector)
Fitted_Proportion <- exp(formula) / (1 + exp(formula))
SC_FVvPDMN_fits <- data.frame(FiedlerVector, Fitted_Proportion)
rm(FiedlerVector, formula, Fitted_Proportion)

@@

``` {r Partition comparison: halves, echo=FALSE, message = FALSE, cache = TRUE}
# Load data
setwd('./Summary_halves/')
temp <- list.files(pattern = "*_finalSummary.csv")
subjList_halves <- sapply(temp, substring, first=1, last=9)
Summaries_halves <- lapply(temp, read.csv)

# Before thresholding, capture within/between daily comparisons for FV vs correlation analysis (only for daily)
Summaries_halves_unthresh <- Summaries_halves

# Load the correlation-based maps from each day for analysis in a subsequent section
temp <- list.files(pattern = "*_corHalves.csv")
Correlation_halves <- lapply(temp, read.csv, header = F)

@@

# Select a submatrix with the best-performing subjects to show on the matrix figures
# These will be also displayed on the session matrix
# This way I don't have to recompute stuff
tmp <- data_frame(SubjID = subjList,
                  DailyARI = Halves_PFCComparison[[1]])
best <- tmp %>% top_n(10, wt = DailyARI) 
bestindx <- substr(subjList_halves,1,6) %in% best$SubjID

@@

# Get the same subsection of participants for the correlation plots
Correlation_halves_plot <- Correlation_halves[bestindx]

# Save unthresholded subjects for comparing and plotting against correlation maps
unthreshComm_PFC_halves_plot <- lapply(Summaries_halves_unthresh[bestindx], "[", i = !posteriorIndx, j =)
unthreshComm_PFC_halves <- lapply(Summaries_halves_unthresh, "[", i = !posteriorIndx, j =)
```

@@

```{r Meta-analysis ROIs (Fig. 1), out.width = "50%", fig.align = "center", fig.cap= "Figure 1. Template atlas from Glasser et al. (2016) (top), as well as the common and unique brain regions associated with DMN and subjective value (bottom). Overlapping ROIs (in blue) were defined as the common brain regions that were significantly present in their respective literatures, while a single DMN-specific region (7m, in red) was identified from a permutation analysis comparing these literatures."}
# Change to inflated eventually
include_graphics("./Images/ROIS3.png")
```

@@

``` {r Partition comparison: all cross-method agreement (Fig. 3), fig.align="center", fig.width=3.5, fig.height=3.5, echo=FALSE, message = FALSE, fig.cap = "Figure 3. Distribution of ARI indices when comparing modularity and spectral partitioning. The distribution shows overall high agreement. (Will probably remove this figure)"}
RI_within_plot <- ggplot(data = RI_all_within, aes(Index)) + 
        geom_density(fill = Cols[3]) + 
        xlim(0,1) + 
        labs(x = "Adj. Rand Index") +
        theme_classic()
RI_within_plot
```

``` {r Partition comparison: all 2 (Fig. 4), fig.align="center", out.width = "40%", fig.cap = "Figure 4. Similarity matrix showing ARI values among all subjects for PCC (lower triangle) and mPFC (upper triangle) separately. PCC is well aligned across individuals, while mPFC shows clear topographical heterogeneity.", echo=FALSE, message = FALSE}
par(xpd=T)
corrplot(RI_PCC,
         is.corr = F, 
         method = "color",
         type = "lower", 
         tl.pos = "n", 
         tl.cex = 0.1, 
         #cl.lim = c(0,1),
         cl.length = 3,
         addgrid.col = "grey99",
         cl.pos = "r",
         mar = c(1,1,2,0))
corrplot(RI_PFC, 
         is.corr = F, 
         method = "color", 
         type = "upper", 
         tl.pos = "n", 
         tl.cex = 0.1,
         cl.pos = "n",
         addgrid.col = "grey90",
         mar = c(1,1,2,0), 
         add = T)
segments(0.5,0.5,0.5,100.5, lwd = 2)
segments(0.5,0.5,100.5,0.5, lwd = 2)
segments(0.5,100.5,100.5,100.5, lwd = 2)
segments(100.5,0.5,100.5,100.5, lwd = 2)
mtext(expression(bold("Subject Partitions")), line = 3)
mtext(expression(bold("Subject Partitions")), side = 2, line = -0.8)
mtext(expression(bold("mPFC")), line = 2, at = par("usr")[1]+0.73*diff(par("usr")[1:2]), col = "steelblue4")
mtext(expression(bold("PCC")), side = 1, line = 4, at = par("usr")[1]+0.18*diff(par("usr")[1:2]), col = "steelblue4")

@@

``` {r Partition comparison: halves (Fig. 5), fig.align="center", out.width = "60%", fig.cap = "Figure 5. Similarity matrices for 10 example participants showing pattern agreement across days for the whole partition (left), and for PCC and mPFC separately (right). These figures show high agreement within (but not between) subjects, with mPFC again showing significant variability.", echo=FALSE, message = FALSE}
# plots
par(mfrow=c(1,2))
corrplot(RI_all_between_halves_plot, 
         is.corr = F, 
         method = "color",
         addgrid.col = "grey90",
         tl.pos = "n", 
         tl.col = "black",
         tl.cex = 0.1,
         cl.pos = "n",
         #cl.lim = c(0,1),
         cl.length = 3,
         mar = c(1.1,1.1,1.1,1.1))
# segments(0.5,0.5,0.5,20.5, lwd = 2)
# segments(0.5,0.5,20.5,0.5, lwd = 2)
# segments(0.5,20.5,20.5,20.5, lwd = 2)
# segments(20.5,0.5,20.5,20.5, lwd = 2)
mtext(expression(bold("Subjects (Day 1 and Day 2)")), line = 1)
mtext(expression(bold("Subjects (Day 1 and Day 2)")), side = 2, line = 3)
corrplot(RI_PCC_halves_plot, 
         is.corr = F,     
         method = "color",
         type = "lower", 
         tl.pos = "n", 
         #cl.lim = c(0,1),
         cl.pos = "r",
         addgrid.col = "grey90",
         cl.length = 3)
corrplot(RI_PFC_halves_plot, 
         is.corr = F, 
         method = "color",
         type = "upper", 
         tl.pos = "n", 
         cl.pos = "n", 
         addgrid.col = "grey90",
         add = T)
mtext(expression(bold("Subjects (Day 1 and Day 2)")), line = 1)
mtext(expression(bold("mPFC")), line = -0.15, at = par("usr")[1]+0.8*diff(par("usr")[1:2]), col = "steelblue4")
mtext(expression(bold("PCC")), side = 1, line = 0.6, at = par("usr")[1]+0.09*diff(par("usr")[1:2]), col = "steelblue4")
```

``` {r Partition comparison: halves ratios (Fig. 6), fig.align="center", fig.width=3, fig.height=3, fig.cap = "Figure 6. mPFC displays higher within-subject agreement than between subjeccts, as evidenced by a high within/between subject mean ARI. PCC also shows some level of topographical idiosyncrasy (ratio > 1), but significantly lower than mPFC.", echo=FALSE, message = FALSE}
# plot
ggplot(data = Halves_RIRatios_summary, aes(Region, RI, fill = Region)) + 
  geom_boxplot(show.legend = F) +
  scale_fill_manual(values = Cols[seq(2)]) + 
  ylim(0, 10) +
  geom_hline(yintercept = 1) +
  labs(y = "ARI Ratio", x = "") + 
  theme_classic(base_size = 14)
```

``` {r Partition comparison: session similarity matrices (Fig. 7), fig.align="center", out.width = "60%", fig.cap = "Figure 7. Similarity matrices showing pattern agreement across sessions for the whole partition (left), and for PCC and mPFC separately (right) (10 example subjects). The pattern from the daily analysis is preserved, with marked individuality for mPFC, but not PCC.", echo=FALSE, message = FALSE}
# plot
par(mfrow=c(1,2))
corrplot(RI_all_between_sess_plot, 
         is.corr = F, 
         method = "color", 
         tl.pos = "n", 
         tl.cex = 0.5,
         tl.col = "black", 
         #cl.lim = c(-0.03,1),
         cl.pos = "n",
         cl.length = 3,
         mar = c(1.1,1.1,1.1,1.1), 
         addgrid.col = "grey90")
# segments(0.5,0.5,0.5,40.5, lwd = 2)
# segments(0.5,0.5,40.5,0.5, lwd = 2)
# segments(0.5,40.5,40.5,40.5, lwd = 2)
# segments(40.5,0.5,40.5,40.5, lwd = 2)
mtext(expression(bold("Subjects (Session)")), line = 1)
mtext(expression(bold("Subjects (Session)")), side = 2, line = 3)
corrplot(RI_PCC_sess_plot, 
         is.corr = F, 
         method = "color", 
         type = "lower", 
         tl.pos = "n", 
         tl.cex = 0.5,
         tl.col = "black", 
         #cl.lim = c(0,1),
         cl.length = 3,
         cl.pos = "r", 
         addgrid.col = "grey90")
# segments(0.5,0.5,0.5,20.5, lwd = 2)
# segments(0.5,0.5,20.5,0.5, lwd = 2)
# segments(0.5,20.5,20.5,20.5, lwd = 2)
# segments(20.5,0.5,20.5,20.5, lwd = 2)
corrplot(RI_PFC_sess_plot, 
         is.corr = F, 
         method = "color", 
         type = "upper", 
         tl.pos = "n", 
         tl.col = "black", 
         cl.pos = "n", 
         addgrid.col = "grey90",
         add = T)
mtext(expression(bold("Subjects (Session)")), line = 1)
mtext(expression(bold("mPFC")), line = 0, at = par("usr")[1]+0.8*diff(par("usr")[1:2]), col = "steelblue4")
mtext(expression(bold("PCC")), side = 1, line = 1, at = par("usr")[1]+0.09*diff(par("usr")[1:2]), col = "steelblue4")
```

``` {r Partition comparison: session ratios (Fig. 8), fig.align="center", fig.width=3, fig.height=3, fig.cap = "Figure 8. Whole group ratio between within- and between-subject ARI for mPFC and PCC based on sessions. Consistent with the daily analysis, both regions show idiosyncrasy, with mPFC being significantly more subject-specific.", echo=FALSE, message = FALSE}
ggplot(data = Sess_RIRatios_summary, aes(Region, RI, fill = Region)) + 
  geom_boxplot(show.legend = F) +
  scale_fill_manual(values = Cols[seq(2)]) + 
  ylim(0, NA) +
  geom_hline(yintercept = 1) +
  labs(y = "ARI Ratio", x = "") + 
  theme_classic(base_size = 14)
```

``` {r Stability per subject: Overall (Fig. 9), fig.align="center", fig.width=5, fig.height=3, fig.cap = "Figure 9. ARI between communities computed at each sliding epoch and the original partition for all subjects (left), as well as the distribution of ARI standard deviations per subject (right).", echo=FALSE, message = FALSE}
# TAKE THE TIME TO BRING THE GGPLOT DEFINITION DOWN HERE EVENTUALLY
grid.arrange(SC_plot, SC_sd_plot, ncol = 2)
```

``` {r Stability per subject: PCC vs mPFC (Fig 10), fig.align="center", fig.width=5, fig.height=3, fig.cap = "Figure 10. ARI between each window and the original pattern for PCC and mPFC separately (left), and the mean per-subject ARI for the whole group (middle). Regardless of the mean ARI, standard deviation remained low for both regions (right).", echo=FALSE, message = FALSE}

@@

``` {r Stability per subject: Fiedler vector vs prop. DMN plot (Fig 11), fig.align="center", fig.width=3, fig.height=3, fig.cap = "Figure 11. Relationship between the magnitude of Fiedler vector values and the proportion of affiliations of a vertex with DMN throughout 37 sliding windows. Grey lines denote each subject's association, while the black line shows the fit from a mixed effects logistic regression.", echo=FALSE, message = FALSE}
# Fiedler Vector x proportion of times a vertex was affiliated with DMN
SC_FVvPDMN_plot <- ggplot(data = allSummaries) +
  geom_smooth(aes(FiedlerVec, slidePropDMN, group = SubjID), color = "gray", fill = "gray", show.legend = F, alpha = 0.3) +
  #geom_line(aes(FiedlerVec, FittedVals), alpha = 1, size = 3) +
  geom_line(data = SC_FVvPDMN_fits, aes(FiedlerVector, Fitted_Proportion), lwd = 3) +
  labs(x = "Fiedler Vector Values", y = "Proportion of DMN Affiliations") +
  scale_y_continuous(limits = c(0,1)) +
  theme_classic()

@@

``` {r Noise Effects: tSNR Comparison (Fig. 12), fig.align="center", fig.width=3, fig.height=3, fig.cap = "Figure 12. Mean tSNR for mPFC and PCC across participants. This measure was derived from the minimally preprocessed fMRI data from the HCP, and thus shows the base level of reltive noise in each region.", echo=FALSE, message = FALSE}
# Plot the mPFC SNR vs PCC SNR for each subject (one figure containing all subjects)
snrmeanComp_plot <- ggplot(data = SNR_meanComp$Values, aes(Region, SNR, fill = Region)) +
  geom_boxplot(show.legend = F) +
  scale_fill_manual(values = Cols[seq(2)]) +
  labs(x = "", y = "tSNR") +
  theme(text = element_text(size=35)) +
  theme_classic()
snrmeanComp_plot
```

@@

``` {r Noise Effects: R-sqd vs tSNR (Fig. 14), fig.align="center", fig.width=5, fig.height=3, fig.cap = "Figure 14. Vertex tSNR values across all subjects are correlated with their position along the z-axis in mPFC, with vmPFC showing the lowest tSNR (left). However, R-square values do not show this strong relationship (right), suggesting that the coupling of each vertex is not necessarily influenced by signal noise.", echo=FALSE, message = FALSE}
# grid.arrange(v6, v7, ncol = 2)
# par(mfrow = c(1,2))
# smoothScatter(allVariance[allVariance$Region == "mPFC",]$Rsquared, allVariance[allVariance$Region == "mPFC",]$tempZ,
#               xlab = "R-squared Value",
#               ylab = "Z-Coordinate")
# 
# smoothScatter(allVariance[allVariance$Region == "mPFC",]$varCoeff, allVariance[allVariance$Region == "mPFC",]$tempZ,
#               xlab = "Coefficient of Variation (SNR)",
#               ylab = "")
